Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-06 analyses/2015_06_27_ResTime.Rmd

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("vegan") 
require("vegan") 
#install.packages("moments")
require("moments")
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
par(mfrow=c(2, 2))

plot(h.tau, m.tau, xlab="Ecosystem residence time", log="xy",
     ylab="Individual residence Time", col='darkmagenta')

plot(h.tau, t.tau, xlab="Ecosystem residence time", log="xy",
     ylab="Particle residence Time", col='grey')

plot(h.tau, r.tau, xlab="Ecosystem residence time", log="xy",
     ylab="Resource residence Time", col='darkcyan')
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
par(mfrow=c(1, 2))

num.sims <- max(sim.data$sim)
colors <- rainbow(num.sims)

@@

  if (i == 1){
    plot(x, y, xlab="Ecosystem residence time", log="xy",
    ylab="Species richness", xlim = c(20, 6000), ylim = c(2, 50),
    main = "S vs. Tau", col=colors[i])
    lines(x, y, col=colors[i])
    }
  else{
    points(x, y, col=colors[i])
    lines(x, y, col=colors[i])
    }
}
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
par(mfrow=c(1, 2))

@@

maint <- (S*sim.data$avg.per.capita.maint)/N
plot(h.tau, maint, xlab="Ecosystem residence time", log="xy",
     ylab="Maintenance", 
     main = "Per capita maintenance vs. Tau",
     col='darkolivegreen')
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
par(mfrow=c(2, 2))

@@

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
par(mfrow=c(2, 2))

@@

#ct <- 1
#for(rtd in res.RTDs){
#  if(any(is.na(rtd)) == FALSE){
#    lines(density(log(rtd), bw = 0.2), col = colors[ct])
#    r.skews <- c(r.skews, skewness(rtd))
#    r.means <- c(r.means, mean(rtd))
#    }
#  ct = ct + 1
#}
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=6, fig.height=6}
par(mfrow=c(1, 1))

@@

legend("topright", legend = c(paste("Tracers: slope=",t.slope,", p=",t.p), paste("Individuals: slope=",i.slope,", p=",i.p)), pch=19, bty = "n", col = c("grey", "darkmagenta"))
```

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("vegan") 
require("vegan") 
#install.packages("moments")
require("moments")
library(ggplot2)
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}

source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")

png(filename = '~/GitHub/hydrobide/results/figs/ComparingResTimes.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

#par(mfrow=c(2, 2))
p1 <- ggplot(data=NULL, aes(x=h.tau, y=t.tau)) +
  geom_point(color="cyan") +
  labs(x= expression(tau), y="Residence Time") +
  labs(title="Tracers") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p2 <- ggplot(data=NULL, aes(x=h.tau, y=m.tau)) +
  geom_point(color="magenta") +
  labs(x= expression(tau), y=" ") +
  labs(title="Individuals") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p3 <- ggplot(data=NULL, aes(x=h.tau, y=r.tau)) +
  geom_point(color="chartreuse") +
  labs(x= expression(tau), y=" ") +
  labs(title="Resources") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 200)) +
  coord_fixed(ratio = 2.38) +
  theme_black()

multiplot(p1, p2, p3, cols=3)

dev.off()
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}

png(filename = '~/GitHub/hydrobide/results/figs/NandS_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(1, 2))
num.sims <- max(sim.data$sim)
colors <- rainbow(num.sims)

@@

  if (i == 1){
    plot(x, y, xlab="Ecosystem residence time", log="xy",
    ylab="Species richness", xlim = c(20, 6000), ylim = c(2, 50),
    main = "S vs. Tau", col=colors[i])
    lines(x, y, col=colors[i])
    }
  else{
    points(x, y, col=colors[i])
    lines(x, y, col=colors[i])
    }
}

dev.off()

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}

png(filename = '~/GitHub/hydrobide/results/figs/Growth_and_Maint.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(1, 2))

@@

maint <- (S*sim.data$avg.per.capita.maint)/N
plot(h.tau, maint, xlab="Ecosystem residence time", log="xy",
     ylab="Maintenance", 
     main = "Per capita maintenance vs. Tau",
     col='darkolivegreen')

dev.off()
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
png(filename = '~/GitHub/hydrobide/results/figs/Diversity_vs_N.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(2, 2))

@@

dev.off()
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
png(filename = '~/GitHub/hydrobide/results/figs/RTDs.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(2, 2))

@@

#ct <- 1
#for(rtd in res.RTDs){
#  if(any(is.na(rtd)) == FALSE){
#    lines(density(log(rtd), bw = 0.2), col = colors[ct])
#    r.skews <- c(r.skews, skewness(rtd))
#    r.means <- c(r.means, mean(rtd))
#    }
#  ct = ct + 1
#}

dev.off()
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=6, fig.height=6}

png(filename = '~/GitHub/hydrobide/results/figs/RTD_shifts.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(1, 1))

@@

legend("topright", legend = c(paste("Tracers: slope=",t.slope,", p=",t.p), paste("Individuals: slope=",i.slope,", p=",i.p)), pch=19, bty = "n", col = c("grey", "darkmagenta"))

dev.off()
```
